\chapter{Introduction}
Autism spectrum disorder (ASD) is a condition that is characterized by a broad range of challenges within different areas such as social skills, speech and nonverbal communication, or by causing repetitive behavior.
In 2014 there were 16.8 occurrences of the ASD diagnosis per 1,000 children, and approximately 1\% of all Danes have an ASD diagnosis\autocite{cdcdata}. 
As ASD is a spectrum disorder, each person diagnosed with it has different strengths and challenges.
This results in people with ASD learning, thinking and solving problems very differently, with ranges from highly skilled and functional to severely challenged. 
Some may require support in their daily lives while others on the spectrum can live entirely independently\autocite{autismspeaks}.

\input{sections/introduction/about-giraf}
\input{sections/introduction/scrum}
\input{sections/introduction/technologies-and-tools.tex}
This section describes the technologies and tools that are used in this project. 
Some of them are used to facilitate the collaboration between all the groups in the GIRAF project while others are just used internally in our group.

\paragraph{Jira}~\\
Jira is a software development tool that is developed by Atlassian and is used for agile software development.
It is possible in Jira to create a backlog of user stories that can then be assigned to a sprint. The user can assign story points to each assignment and assign a user to the user story.
Jira also includes multiple tools for managing and monitoring sprints and their progress.
We used it for our weekly sprints that we had in our group.

\paragraph{Adobe XD}~\\
Adobe XD is a program developed by Adobe that used to create prototypes.
It is a simple program that is easy to pick up and create simple designs in.
Adobe XD makes it easy to reuse components in multiple design projects and to collaborate with others.

\paragraph{GitHub}~\\
GitHub is a development platform that makes it possible for multiple people to collaborate on a project. 
All of the code in the GIRAF project is hosted on GitHub.
The issue and project features are used to create and assign user stories to the different groups that are working on the GIRAF project and to manage the sprints. 
The GIRAF wiki is also hosted on GitHub.

\paragraph{Slack}~\\
Slack is a Collaboration hub where users can create a workspace that they can invite their collaborators to.
It is then possible to create multiple channels. The collaborators can then choose which channel they want to join.
Slack has been used for all communication across the GIRAF project.

\input{sections/introduction/before-sprint-1}
