\section{The process in our group}

The structure of the work process in our own group was inspired by the Scrum process.
We only chose certain aspects of Scrum to reduce the amount of meetings we needed to have internally in our group. 
Since we all met everyday in the group room and we had a lot of meetings related to the GIRAF project we found that this solution worked the best for us.
From Scrum we chose these aspect to use in our process.

 \begin{itemize}
    \item Product Backlog
    \item Sprint Backlog
    \item Product Increment
    \item Sprints
    \item Sprint planning
    \item Planning poker
    \item Product owner
    \item Retrospectives
 \end{itemize}
To organize all our internal tasks we used the product backlog, which was handled by Jira.
In there, each member of the group could add tasks or user stories.
This differs from Scrum where only the Product Owner would handle the Product Backlog.
The reason for this is that we decided that with each new sprint there would be appointed a new Product Owner which responsibility was solely to decide which user stories and tasks should be added to our new Sprint Backlog and in what priority.
This was because we internally did not have a customer to contact, instead the person appointed Product Owner also worked as a regular developer with the job as Product owner as an user story.
\\\\
Before a new sprint would start the previous Product Owner would have chosen and prioritized user stories for the new Sprint Backlog.
The whole group would then partake in planning poker where we would estimate how much each task would take to complete.
Afterwards each member would pick some user stories until all user stories was taken.
We would always try to distribute the user stories evenly so that each member had the same amount of story points.
\\\\
Our internal sprints were one week long compared to the sprints in the GIRAF project which ranged between two and 4 weeks.
\\\\
At the end of a sprint we would have a retrospective meeting where each member would tell how far they got with their user stories and what could have been better so that they would have been more productive.
We later decided to stop holding retrospective meetings because the feedback was always the same and eventually no one had anything worthy of an extra meeting to add to the process.


