\section{Sprint introduction}
Sprint 3 began on the 9th of April, and lasted until the 29th of April.
As with the previous sprint, the sprint introduction started with a small presentation of the following sprint. 
The presentation also included a presentation of the most important features in the product backlog.
After the presentation the development groups looked through the backlog, and requested to be assigned certain user stories by the PO group.

\subsection{The goals and visions for the GIRAF project}
The goals for the following sprint are:

\begin{itemize}
    \item Finish sprint 1 and sprint 2 user stories
    \item Add functionality to remove activities
    \item Implement a way to rearrange pictograms
    \item New font throughout the application
    \item Implementation of guardian and citizen mode
\end{itemize}

\noindent
As for the product vision for the GIRAF project this semester, we decided to remove the requirement for offline availability. 
This feature was simply too big to be implemented within the two following sprints, as we also had other more important features to ensure satisfactory functionality for the customer.

\subsection{The goals for the PO group}\label{sprint-3-po-goals}
The goals for the PO group included the user stories weekplanner\#133, weekplanner\#92 and weekplanner\#125 as seen on \autoref{item:userstories-sprint-3}.

\begin{itemize}\label{item:userstories-sprint-3}
    \item Weekplanner\#133 - "As a guardian I would like to be able to logout when I'm on the choose citizen page so that I can return to the login page"
    \item Weekplanner\#92 - "As a developer I would like the application to use a default font so that I can easily change it"
    \item Weekplanner\#125 - "Exception thrown when rendering WeekPlanScreen, issue \#44"
\end{itemize}
\noindent
Besides the user stories we still needed to complete the PO tasks that we have every sprint.
We had a goal to conduct a usability test with the customers to test the application and to get feedback on the design of new prototypes.
Additionally, we needed to prepare the release for sprint 3 and prepare an introduction for sprint 4.

\begin{table}[H]
    \centering
    \begin{tabular}{|l|l|}
    \hline
    Goals:                                   \\ \hline
    Implement weekplanner\#92               \\ \hline
    Implement weekplanner\#125              \\ \hline
    Implement weekplanner\#133              \\ \hline
    Conduct a usability test                 \\ \hline
    Prepare a release                          \\ \hline
    Prepare introduction for sprint 4                         \\ \hline
    \end{tabular}
    \caption{Goals for the PO group in sprint 3}
    \label{PO-goal-sprint-3}
\end{table}
