\section{GIRAF and skill groups}
GIRAF 2019 differed from previous years in that it was the first to employ skill groups.
Skill groups were introduced to facilitate full stack development, meaning all development groups should have knowledge in every area of the application.
A person from each group would be appointed as the one primarily responsible for an area of expertise, and one would be appointed as an alternate in case of sickness.
There was a skill group dedicated to each of the following areas:
\begin{itemize}
    \item Front end
    \item Back end
    \item Server
\end{itemize} 
\noindent
Initially, all groups seemed to work well. 
Meetings were organized regularly, however, some of the skill groups lost their importance as the project progressed.
After the decision was made to change to Flutter, and the design guide had been discussed, the front end group became increasingly irrelevant.
This was most likely due to the purpose of the group being poorly defined.
For the semester, the priority of the front end group had been purely design.
This proved to make the group irrelevant in the long term.
In order to better take advantage of the front end group, a better purpose should be defined.
Instead of simply making decisions relating to design, the front end skill group should have focused more on implementation details in Flutter as well, and organizing hackathons related to front end development.
This would serve to keep the group relevant, and provide a good source of knowledge for developers.
\\\\
The server skill group encountered a different problem.
As the project progressed, it became more insular with fewer developers feeling they could contribute.
The reason for this was hard to define.
It could be caused by the GIRAF project lacking developers with an interest in or knowledge of the subject.
It could also be caused by a smaller, more passionate group of developers wanting to focus on this aspect, and the rest being content with them leading the skill group.
In order to ensure that the knowledge is spread more evenly, an effort should be made within the group to catch everyone up.
An alternative could be to ensure that the server skill group only consisted of the developers interested in it, rather than forcing a person from each group to participate. 
This would go against the spirit of full stack development, however.
The purpose of requiring one participant from each development group was to ensure a feeling of ownership, responsibility and knowledge of all areas, which would be lost.
\\\\
The back end skill group was the one that fulfilled its purpose the best.
It continually held meetings throughout the duration of the project, knowledge was spread fairly evenly between participants, and it did not become largely irrelevant.
The back end group organized a hackathon, in which the skill group got together for a full day to complete tasks related to the back end.
A description of this hackathon can be found in \autoref{collab:back-end}.
This worked well, and should be considered for other skill groups if this concept were to be used again.
\\\\
Even though our usage of skill groups might have had some issues, we still believed it to be superior to the alternative of strictly delegating areas of expertise to different groups.
When a group is capable of implementing a full user story without it needing to be divided into parts, it can lead to a more cohesive application.
At the same time, being familiar with all areas helps to create a feeling of responsibility and ownership for the application in all developers, leading to a better product.
