\section{Sprint introduction}
Sprint 2 began on the 18th of March, and lasted until the 8th of April.
As with the first sprint planning conducted for the GIRAF project described in \autoref{sprint-1-planning}, all participating teams gathered to get an understanding of what would happen in the sprint.
This sprint planning differed quite a bit, however.
Based on feedback from the development groups, the process group had decided that this meeting should primarily function as an introduction where the goals of the sprint and user stories should be presented by the PO group.

\subsection{The goals and visions for the GIRAF project}
With the recent switch of framework for frontend development, we were left with a system that had less functionality than when we started the previous sprint.
As a result of this, we decided on the following goals:
\begin{itemize}
    \item Achieve a foundation of functionality to make the system usable again
    \item Improve the graphical user interface in the week planner as specified through the prototypes in accordance with the new framework, Flutter.
\end{itemize}
Some development groups were still working on user stories from sprint 1, as there was not enough time left to complete them after the change of framework.
This served as a key point for creation of the sprint backlog.
The most important user stories were those the developers were already working on, but had not completed. 
\\\\
User story selection would differ from the method used during the first sprint, as it was not carried out during the actual planning meeting.
As this meeting was mainly supposed to be an introduction, different teams were allowed to pick an open, highly prioritised user story after discussing them once the meeting had concluded.
This meant that the PO group did not have to send a representative to each group during planning, but the different groups should approach the PO group for discussion and confirmation of stories when ready.
However, as long as a group had an unfinished story, that story should be the one they focused on.
This meant that the following stories relating to basic functionality of the week planner were carried into sprint 2:
\begin{itemize}
    \item Login functionality
    \item Week plan view
    \item Navigation
    \item Search pictograms
\end{itemize}
When a new story was selected, the groups should initially choose one of the following highly prioritized stories:
\begin{itemize}
    \item Update status of activities
    \item Swap between citizen and guardian mode and prompt the user for a password when needed
    \item Reorganizing the order of activities
    \item Show details of an activity
\end{itemize}
When a group finishes implementing their user story during the sprint, they should discuss if they had time to implement a new user story before the sprint ended. They should then present their chosen user story to the PO group and get a confirmation.

\subsubsection{The goals for the PO group}
The primary goal for our group this sprint was to keep working on prototypes and implement the user stories assigned to our group.
The two user stories were weekplanner \# 44 and weekplanner \#43 which were:
\begin{itemize}
 \item "As a citizen I would like to be able to view my week plan so that I know what is going to happen" 
 \item "As a guardian I would like to be able to view a given citizen's week plan so that I can get an overview of what is happening this week for them"
\end{itemize}
We also needed to prepare a release, where we decided which user stories should be in the release, based on whether or not they adequately fulfilled their requirements.
The release should also have a usability test with the customers.
The preparations for sprint 3 included preparing user stories, prioritizing them and making sure that the prototypes were up to date.
\begin{table}[H]
    \centering
    \begin{tabular}{|l|l|}
    \hline
    Goals:                                   \\ \hline
    Implement weekplanner \#44               \\ \hline
    Implement weekplanner \#43               \\ \hline
    Prepare release                          \\ \hline
    Conduct a usability test                   \\ \hline
    Prepare sprint 3                         \\ \hline
    \end{tabular}
    \caption{Goals for the PO group in sprint 2}
    \label{PO-goal-sprint-2}
\end{table}
\todo{Maybe goals should be presented in a different way?}
