\section{Usability test 9/4}
Unfortunately, no customers were able to show up, and hereby we were unable to perform a usability test.
This gave us some time to reflect on our contact with the customers and how we could improve.
\\\\
We sent our first email with dates for all the meetings for the entire semester on March 19th and a reminder on April 2nd.
In both emails we asked for them to respond if they were available, to which only two customers answered. 
One customer initially responded on March 21st, saying that they were available at all dates. 
The day before the usability test, however, that customer had to cancel because of personal issues.
The second customer answered that they were unable to show up to the April meeting, the day before it was meant to take place.
\\\\
There were still four other customers who were invited, but did not reply with an answer, which had also happened to one of the previous PO group.
Since no one had responded, we assumed that no customers would show up.
A customer showed up at Cassiopeia, however, and the PO group was not even at the university at that time. 
As we had gotten no answers we prepared for the usability test and assumed that one representative might show up to avoid the same situation.
Unfortunately, no one did.
\\\\
This episode caused us to reflect further on how we handle these invitations.
For the next usability test, we will still send out invitations and reminders through email, but approximately a week before it will take place, we will call all the customers to get a definitive answer regarding whether or not they are available. 
\\\\
As this was the first sprint using Flutter, the functionality of the release available to test was limited. 
For this reason we chose to not invite the customers for another usability test before May 2nd, when the third sprint ends.
This choice was also based on the expectation that the weekplannner would have more functionality to test at this time.
