\chapter*{Preface\markboth{Preface}{Preface}}\label{ch:preface}
\addcontentsline{toc}{chapter}{Preface}
This report was written for the 6th semester of the Software Engineering degree on Aalborg University by group SW610F19. 
\\\\
The main purpose of this semester was to learn how to collaborate across multiple groups on an existing codebase. The codebase we worked on was for an application called GIRAF which is intended to aid people diagnosed with autism, where the main focus for our semester was to further develop the weekplanner application. The development team consisted of 7 groups with 4-6 students per group, and together we had the responsibility for the overall product. 
\\\\
The different groups had different areas of responsibility where we took the role as the product owner group, meaning that we had the final say for the decisions regarding the development of the application. We also had a group responsible for the process used, while the rest of the groups worked as full stack teams. 
\\\\
For references to the different sources used we have included information about the author, publisher, year of release and title name. For web pages we have included url and the date for when it was last accessed.
\\\\
The GitHub page with the different repositories can be found on the \href{https://github.com/aau-giraf}{GIRAF wiki page}. The prototypes that we created can be found in the \href{https://github.com/aau-giraf/wiki/tree/master/design_guide/prototypes}{GIRAF design guide}.
\\\\
A summary of the project can be found in the \autoref{appendix:project-summary}. For information about the experiences gained from being the product owner group as well as advice for future product owners, we recommend looking at \autoref{appendix:PO-advice}
\newpage
\vspace{\baselineskip}\hfill Aalborg Universitet, May 28, 2018
\vfill\noindent
\begin{minipage}[b]{0.45\textwidth}
 \centering
 \rule{\textwidth}{0.8pt}\\
  Andreas Stenshøj\\
 {\footnotesize <astens16@student.aau.dk>}
\end{minipage}
\hfill
\begin{minipage}[b]{0.45\textwidth}
 \centering
 \rule{\textwidth}{0.8pt}\\
  Daniel Moesgaard Andersen\\
 {\footnotesize <dand16@student.aau.dk>}
\end{minipage}
\vspace{3\baselineskip}

\vfill\noindent
\begin{minipage}[b]{0.45\textwidth}
 \centering
 \rule{\textwidth}{0.8pt}\\
  Frederik Valdemar Schrøder\\
 {\footnotesize <fschra16@student.aau.dk>}
\end{minipage}
\hfill
\begin{minipage}[b]{0.45\textwidth}
 \centering
 \rule{\textwidth}{0.8pt}\\
  Jens Petur Tróndarson\\
 {\footnotesize <jtrand16@student.aau.dk>}
\end{minipage}
\vspace{3\baselineskip}

\vfill\noindent
\begin{minipage}[b]{0.45\textwidth}
 \centering
  \rule{\textwidth}{0.8pt}\\
  Mathias Møller Lybech\\
 {\footnotesize <mlybec16@student.aau.dk>}
\end{minipage}
\hfill
\begin{minipage}[b]{0.45\textwidth}
 \centering
 \rule{\textwidth}{0.8pt}
  Rasmus Bundgaard Eduardsen\\
 {\footnotesize <reduar16@student.aau.dk>}
\end{minipage}
