\chapter{Conclusion}
In this chapter we will be evaluating how well the process worked for us, the state of the application and whether we achieved the goals set in our product vision.

\section{Evaluating the process}
As mentioned in \autoref{the-giraf-process}, GIRAF used a modified version of Scrum where some of the concepts from Scrum were used.
Overall the impression was that the process worked quite well for all groups, as there was not made any drastic changes during the semester.
Likewise, all groups finished most of the assigned user stories for each sprint and the productivity was generally good throughout the semester.
The only minor changes that were made from sprint to sprint were based on the feedback from each retrospective, and we ended up with a very efficient process in the final sprint, where we felt that we had a good overview of what was happening in the project.

\section{Final state of GIRAF}
As mentioned in \autoref{change-of-framework}, we changed framework to Flutter and rebuilt the application to make development on Linux possible.
Therefore, we spent a lot of time reimplementing the same functionalities as they had in 2018.
In the final sprint, we implemented some new features that did not exist prior to this year, such as:
\begin{itemize}
    \item Manipulating multiple activities at the same time.
    \item Adding pictograms from gallery to the database.
    \item Deleting weekplans
    \item Adding timers to the activities
    \item Faster pictogram loading with caching
\end{itemize}
A final list of all features can be found in \todo{Autoref til appendix afsnit.}

\section{Evaluating the product vision}
In \autoref{sec:introduction-product-vision} we defined the following goals for the product vision:
\begin{itemize}
    \item Stability
    \item Intuitive design
    \item iOS support
    \item Offline availability
    \item Easier handover for the next generation
\end{itemize}
We would have liked to add even more new features to the application, but as it was expressed numerous times by the customers, stability was important to them if they were to ever use the application.
Achieving a stable and usable weekplanner was the most important goal for us, and from the usability test described in \autoref{usability-test-14-05}, we learned that the customers were very satisfied with the final product.
Therefore, we concluded that we achieved this goal. 
\\\\
Achieving an intuitive design was essential to make the application more usable by the customers.
They were impressed with how easily they understood how to use the different functionalities available in the application, so this goal was also achieved. They mentioned GIRAF was easier to use than previously tested applications.
\\\\
The next goal from our product vision was to to have the application available on iOS since many citizens are using iPads.
This goal is achieved since we switched to Flutter which can compile to iOS.
\\\\
The customers requested offline functionality for the application.
However, this quickly became unrealistic after we switched the framework to Flutter.
We simply did not have time to focus on this goal since we prioritized other functionalities to achieve a minimum viable product, and thus it was not completed.
\\\\
The final goal was to make it easy and accessible for the next generation of GIRAF students to get started.
For the final sprint we focused on documenting every important part of the project and the \href{https://github.com/aau-giraf/wiki}{GIRAF wiki} page on GitHub is now filled with information about the project. In addition to the general information we created a PO handbook, which can be found in the GIRAF wiki and in \autoref{appendix:PO-advice}, to ensure a better start for the next generation of GIRAF product owners.
